Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-11 emsoft-2019/related.tex
related work additions

\citet{Anta10} take an existing controller and its implementation, derive safe
bounds from the controller under which stability is guaranteed and verify that
the implementation in fixed-point arithmetic satisfies this error bound.
Similarly, \citet{ParkPSL17} takes an existing floating-point controller
implementation, reconstructs the controller and verifies that roundoff errors
due to finite precision remain below a user-given error bound.

@@

% finite-precision only
\paragraph{Finite-Precision Optimization}
General-purpose techniques for synthesizing fixed-point implementations of 
arithmetic expressions have been developed in the space of embedded systems,
where resource efficiency is generally important.
Some work has used dynamic analyses for estimating
errors~\cite{Gaffar2004,Mallik2007}, which, however, do not provide guarantees.
Several approaches~\cite{Lee2006,Osborne2007,Kinsman2009,Pang2011} use sound
error analysis techniques, similar to the ones implemented in the tool Daisy
which we use.

>>>>

\citet{Anta10} take an existing controller and its implementation, derive safe
bounds from the controller under which stability is guaranteed and verify that
the implementation in fixed-point arithmetic satisfies this error bound.
Similarly, \citet{ParkPSL17} takes an existing floating-point controller
implementation, reconstructs the controller and verifies that roundoff errors
due to finite precision remain below a user-given error bound. The LCV tool~\cite{Park2019}
additionally checks that the generated code is equivalent (within an error bound)
to a Simulink block diagram model.

@@

% finite-precision only
\paragraph{Finite-Precision Optimization}
General-purpose techniques for synthesizing fixed-point implementations of 
arithmetic expressions have been developed in the space of embedded systems,
where resource efficiency is generally important.
Some work has used dynamic analyses for estimating
errors~\cite{Gaffar2004,Mallik2007}, which, however, do not provide guarantees.
Several approaches~\cite{Lee2006,Osborne2007,Kinsman2009,Pang2011} use sound
error analysis techniques and perform mixed-precision optimization~\cite{Lee2006,Pang2011},
similar to the approach implemented in the tool Daisy which we use.
